A Comparison of the Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-06-27 mt-marathon.2012/PBML_article.tex
from google doc

\begin{equation}
  score = \sum_{i \in T}(weight_i * score_i) + \sum_{i  \in L} (weight_i * score_i) + weight_{wp} * word-penalty
\end{equation}

@@

\begin{equation}
% score =  Sum_i _member_T(weight_i * score_i)
%    + Sum_i _member_L(weight_i * score_i)
%    + weight_wp * word-penalty
%    + weight_d * score_d
%    + Sum_i _member_R(weight_i * score_i)
%    + future_score
\end{equation}

where $weight_d$ and $score_d$ is the distortion weight and score respectively, R is the set of lexicalized reordering models.

@@

\subsection{New Framework}
The new framework better supports the creation of arbitary feature functions by generalizing all code that deals with feature functions.

Equation (1) becomes Equation (...)
\begin{equation}
%  score = Sum_i _member_FF(weight_i * score_i)
\end{equation}

where FF is the set of feature functions.

Equation (2) becomes Equation (...)
\begin{equation}
%  score =  Sum_i _member_FF(weight_i * score_i)
%  + future_score
\end{equation}

>>>>

\begin{equation}
  score = \sum_{i \in T}(\lambda_i * score_i) + \sum_{i  \in L} (\lambda_i * score_i) + \lambda_{wp} * words
\end{equation}

@@

\begin{equation}
 score =  \sum_{i \in T} (\lambda_i * score_i)
    + \sum_{i \in L} (\lambda_i * score_i)
    + \lambda_{wp} * words
    + \lambda_d * score_d
    + \sum_{i \in R}(\lambda_i * score_i)
    + score_{future}
\end{equation}

where $\lambda_d$ and $score_d$ is the distortion weight and score respectively, $R$ is the set of lexicalized reordering models.

@@

\subsection{New Framework}
The new framework better supports the creation of arbitrary feature functions by generalizing all code that deals with feature functions.

Equation (1) becomes Equation (...)
\begin{equation}
  score = \sum_{i \in FF}(\lambda_i * score_i)
\end{equation}
where $FF$ is the set of feature functions.

Equation (2) becomes Equation (...)
\begin{equation}
  score =  \sum_{i \in FF}(\lambda_i * score_i)
	  + score_{future}
\end{equation}
